Seminar: Organisational and risk analysis

### 2019-03-05 msbframework/msbforts/abstract.tex

This lecture covers the first part of MSB's framework~\cite{%
  MSB2011itm,MSB2011sle,MSB2011p,MSB2011v,MSB2011r%
}, i.e.~ISO 27001.
This part covers how to initialise the work with security in an organisation, 
i.e.~how to set up an Information Security Management System (ISMS).
We will talk about the most important steps in this process.

This lecture covers the remaining part of MSB's material~\cite{%
	MSB2011gap,MSB2011vs,MSB2011us,MSB2011upo,%
	MSB2011pg,MSB2011koa,MSB2011i,MSB2011o,MSB2011g,%
	MSB2011lg,MSB2011ulo,MSB2011kf,MSB2011fa%
}.
This part of the material treats how to run an ISMS\@.
The largest part is the gap analysis, i.e.~finding the gap between the security 
practices in the organisation and the practices recommended by ISO 27000.
The main point of this part is not something done once and never again, an ISMS 
is a continuous process.

>>>>

% $Id$
This lecture covers the remaining part of MSB's material~\cite{%
	MSB2011gap,MSB2011vs,MSB2011us,MSB2011upo,%
	MSB2011pg,MSB2011koa,MSB2011i,MSB2011o,MSB2011g,%
	MSB2011lg,MSB2011ulo,MSB2011kf,MSB2011fa%
}.
This part of the material treats how to run an ISMS\@.
The largest part is the gap analysis, i.e.~finding the gap between the security 
practices in the organisation and the practices recommended by ISO 27000.
The main point of this part is not something done once and never again, an ISMS 
is a continuous process.

### 2019-03-05 risksem/risksem.tex

The seminar is divided into three parts, discussions about your classification
models, using classification models and performing risk analysis on some
information assets that we will identify during the seminar.

>>>>

The seminar is planned to take around 4 hours and is divided into three parts;
discussions about your classification models, using classification models and
performing risk analysis on some information assets that we will identify during
the seminar.
